


\section{Question 1}
\label{part1}

Write a program that extracts 10000 tweets with links from Twitter. 
Reference - http://thomassileo.com/blog/2013/01/25/using-twitter-rest-api-v1-dot-1-with-python/ 
Other resources are available 
Note that only Twitter API 1.1 is currently available; version 1 code will no longer work. 
	
\begin{itemize}
\item Save the tweets URIs, and the mapping to the link(s) each tweet contains 
\item For each \url{t.co} link use ``curl –I –L'' to record the HTTP headers all the way to a terminal HTTP status (i.e. chase down all the redirects)
\item How many unique final URIs? How many duplicate URIs?
\item Build a histogram of how many redirects (every URI will have at least 1) \url {http://en.wikipedia.org/wiki/Histogram}
Build a histogram of HTTP status codes encountered (you’ll have at least 20000: 10000 301s, and 10000+ more)
\end{itemize}
\subsection{Solution}

The following steps were taken to extract tweets from twitter:
\begin{itemize}
	\item Consumer key, consumer secret key, OAUTH token, OAUTH secret token are collected by registering an application 
	in Twitter.
	\item Using above credentials and requests package for python I retrieved tweets from twitter 
	\item Twitter response was saved as json in a local mongodb database.
	\item All redirects are calculated using the requests api and saved in a separate table other then the one we used for saving in tweets.
	\item Unique URI's, duplicate URI's are counted using set function in python.
\end{itemize}
\newpage